### 2012-04-23 sermons/Revelation1:1b-3.tex
Started on new sermon.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
\tableofcontents
\BI
\section*{Notes}
\I  The point of this sermon is:
        \begin{quote} 
        You need to know and obey the Revelation of Jesus Christ.
        \end{quote}

This Scripture prepares us to read and obey the rest of the book.
It does so by telling us what Revelation is about
    and what we must do with it.

In this light, the goal of this sermon is to place a burden on the hearers 
    to know and become familiar with the contents of this book, 
    and to heed the commands given in it.

\section*{Introduction}
\section{The Subject of the Revelation of Jesus Christ}
\I The book of Revelation reveals Jesus Christ.
\subsection{He is God}
\I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
\I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
\I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
                the First and the Last.''}
\I Rev 1:13 \Q{\ldots and in the midst of the seven lampstands One 
                like the Son of Man, \ldots}
\I Rev 3:1, 5:6
            \Q{``These things says He who has the seven Spirits of God 
                and the seven stars: \ldots''}    
            \Q{And I looked, and behold, in the midst of the throne 
                and of the four living creatures, 
                and in the midst of the elders, 
                stood a Lamb as though it had been slain, 
                having seven horns and seven eyes, 
                which are the seven Spirits of God sent out into all the earth.}
\I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
                the Beginning of the creation of God; \ldots}
\I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these things 
                in the churches, I am the Root and the Offspring of David, 
                the Bright and Morning Star.''}
\I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
                in its strength.}

\subsection{He is the Savior}
\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
                in His own blood, \ldots}
\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                I am alive forevermore.}
\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
                and of the four living creatures, and in the midst of the
                elders, stood a Lamb as though it had been slain, \ldots}
\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
                whose names have not been written in the Book of Life
                of the Lamb who was slain from the foundation of the world.}
\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                And to open its seals; \\
                For You were slain, \\
                And have redeemed us to God by Your blood \\
                Out of every tribe and tongue and people and nation, \ldots''}
\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
                To receive power and riches and wisdom, \\
                And strength and honor and glory and blessing!''}
\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
                Be to Him who sits on the throne, \\
                And to the Lamb, forever and ever!''}
\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                the Root of David, has prevailed to open the scroll 
                and to loose its seven seals.''}
\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
                and shuts and no one opens.''}
\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
\I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                for the marriage of the Lamb has come,
                and His wife has made herself ready.''}
\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
                will shepherd them and lead them to living fountains of waters.
                And God will wipe away every tear from their eyes.''}
\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
                and the Lamb are its temple. The city had no need 
                of the sun or of the moon to shine in it, 
                for the glory of God illuminated it. The Lamb is its light.}
\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
                clear as crystal, proceeding from the throne of God 
                and of the Lamb. In the middle of its street, and on either
                of the river, was the tree of life, which bore twelve fruits,
                each tree yielding its fruit every month. 
                The leaves of the tree were for the healing of the nations.}
\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
                and of the Lamb shall be in it, and His servants shall 
                serve Him. They shall see His face, and His name shall be on
                their foreheads.}

\subsection{He is the conquering King}
\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
                even they who pierced Him. And all the tribes of the earth
                will mourn because of Him. Even so, Amen.}
\I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
                and His eyes like a flame of fire; His feet were like brass, 
                as if refined in a furnace, and His voice as the sound of 
                many waters; He had in his right hand seven stars, 
                out of His mouth went a sharp two-edged sword, 
                and His countenance was like the sun shining in its strength.}
\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
                ``Fall on us and hide us from the face of Him who sits on the
                throne and from the wrath of the Lamb! For the great day of His
                wrath has come, and who is able to stand?''}
\I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
                sat One like the Son of Man, having on His head a golden crown, 
                and in His hand a sharp sickle.}
\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
                and the Lamb will overcome them, for He is Lord of lords and
                King of kings; and those who are with Him are called, 
                chosen, and faithful.''}
\I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
                And He who sat on Him was called Faithful and True,
                and in righteousness He judges and makes war.
                His eyes were like a flame of fire, and on His head were
                many crowns. He had a name written that no one knew except
                Himself. He was clothed with a robe dipped with blood,
                and His name is called The Word of God.
                And the armies of heaven, clothed in fine linen, white and
                clean, followed Him on white horses.
                Now out of His mouth goes a sharp sword, that with it He 
                should strike the nations. And He Himself will rule them 
                with a rod of iron. He Himself treads the winepress of the
                fierceness and wrath of Almighty God. And He has on His robe 
                and on His thigh a name written:
                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}

\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
                into the lake of fire.}
            Note: we know this is the Lamb's Book of Life from Rev 13:8.

\section{The Purpose of the Revelation of Jesus Christ}
\subsection{To show}
\I Definition: to expose to the eyes; to explain, to reveal, and to inform.
\I Matthew 16:21 \Q{From that time Jesus began to show to His disciples
                    that He must go to Jerusalem, and suffer many things from
                    the elders and chief priests and scribes, and be killed,
                    and be raised on the third day.}
\I John 20:20 \Q{When He had said this, He showed them His hands and His side.
                Then the disciples were glad when they saw the Lord.}
\I The purpose of Revelation is \emph{communication}, not \emph{confusion}.
\subsubsection{Understanding is expected}
\I Rev 2:7, 11, 17, 29; 3:6, 13, 22 -- the repeated exhortation to the churches
    \Q{He who has an ear, let him hear what the Spirit says to the churches.}
\I Rev 1:3, 22:7 -- we are expected to hear \emph{with understanding} in order
    to obey
    \Q{Blessed is he who reads and those who hear the words of this prophecy,
    and keep those things which are written in it; for the time is near.}
    \Q{Behold, I am coming quickly! Blessed is he who keeps the words 
    of the prophecy of this book.}
\subsubsection{Understanding has been enabled}
\I Some will say that they are not able to understand. This is \emph{not}
    a valid excuse.
\I Has He not given you the Holy Spirit?
\BI \I Was it not the washing of regeneration and renewing of the Holy Spirit
        that saved you? (Titus 3:5)
    \I Were you not born of water and the Spirit? (John 3:5)
    \I Do you not live by the Spirit (thereby putting to death 
        the deeds of the flesh)? (Romans 8:13)
    \I How then can we say that we are unable to hear, and understand,
        what the Spirit says to the churches? \EI
\I Maybe if you were those who had hearts of stone,
    but you have been given a heart of flesh (Ezekiel 36:26).
\I Maybe if you were still futile in your thoughts (Romans 1:21), 
    but you have been given the mind of Christ (1 Corinthians 2:16).
\I In Jesus Christ you have been blessed with every spiritual blessing 
    in the heavenly places in Jesus Christ (Eph 1:3), 
\BI \I including knowing the mystery of His will (Eph 1:9), 
    \I and the dispensation of the fullness of the times (Eph 1:10), \EI
\I so that you can understand, and that you are without excuse.

\subsubsection{Why understanding is not achieved}
\I Why do we still have such trouble understanding?
\I Yes, Revelation is, without a doubt, the most
    controversial, misinterpreted, and misused book of the Bible.
\I The problem is the hardness of our hearts, not the clarity of God's Word.
\I Consider Jesus' disciples,
\BI \I with the Lord 24/7 for 3 years,
    \I Jesus personally taught them that He must be crucified and then 
        rise again,
    \I but the Jesus' death caught them by surprise,
        and they initially didn't believe that He had risen!
    \I How did Jesus characterize two of them, on the Emmaus road?
        \Q{``O foolish ones, and slow of heart to believe in all that the 
            prophets have spoken!''} (Luke 24:25)
    \I And He basically preached the entire Old Testament to them,
        in order that they might finally understand God's plan of redemption. 
    \EI
\I In the same way, we do not understand only because we are either
\BI \I lovers of the world, 
    \I ensnared by sin, 
    \I foolish,
    \I slow of heart to believe, or because 
    \I we have not diligently searched and studied the Scriptures 
        that we might understand God's full plan of redemption. \EI

\subsection{His servants}
\I If you are a Christian, then you are the target audience of Revelation.
    This highlights our need, as His servants, to know His Revelation.
\BI \I Not for the world, but for His saints.
    \I Not primarily for evangelism, but for the edification of the Church.
    \I Not for repentance in the unbeliever, but in the life of the Christian.
\EI
\I This need is further deepened when we consider that 
    ``servant'' is more accurately translated ``slave''.
\BI \I We are the property of Jesus Christ,
    \I owned by Him,
    \I fully subject to His will.
    \I Jesus has the full and complete rights to your life. \EI
\I This means that knowing Revelation 
\BI \I Is not a matter of leisure, or a hobby -- 
        it is a matter of necessity and duty, as Christ's slave.
    \I It is not about enriching yourself, 
        or simply becoming more knowledgeable about the Bible -- 
        it's about being faithful, and obedient.\EI
\I Revelation is \emph{literally} Master Jesus' final instructions 
    to His slaves before His return.
\I And we cannot be the
\BI \I faithful and wise servant (Matt 24:45) who is found faithfully
        carrying out his Master's instructions, or
    \I the servant (Matt 25) who has faithfully used the 2 or 5
        talents entrusted to him by his Master \EI
    apart from knowing and obeying the Revelation of Jesus Christ.

\subsection{Things which must shortly take place}
\I \emph{Transition:} We must make Revelation an urgent, \#1 priority,
    because it informs us of the imminent.
\I If imminent back then, how much more so now!
\I Revelation has \emph{not} been fulfilled:
\BI \I We are not in the new heaven and the new earth.
    \I Death and Hades have not been thrown into the lake of fire.
    \I Sin has not been abolished.
    \I There still remains the final battle against Satan and the world.
    \I The final judgement of sinners and the righteous.
    \I Christ's evaluation of believers. \EI
\I These things are future, but not far off, they are future imminent.
\BI \I The Lord is not slow, He is merciful (2 Peter 3:19)
    \I Nothing is hard for Him, 
        but His judgement would have been far too much for you to bear! \EI
\I The Second Coming is unheralded, it comes without warning.
\BI \I Rev 22:7, 12 \Q{``Behold! I am coming quickly!''}
    \I Rev 16:15 \Q{``Behold! I am coming as a thief''} \EI
\I We must learn from the flood of Noah's time (Matt 24:38-39).
    \Q{``For as in the days before the flood, they were eating and drinking,
    marrying and giving in marriage, until the day that Noah entered
    the ark, and did not know until the flood came and took them all away,
    so also will the coming of the Son of Man be.''} 
\I We must be those who are prepared for His return 
    (Matt 25, parable of the virgins).
\I And we can start on this by reading, understanding, and obeying
    the Revelation of Jesus Christ.

\section{The Authority of the Revelation of Jesus Christ}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{All things that he saw}

\section{The Blessing of the Revelation of Jesus Christ}
\EI
\end{document}

>>>>

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Revelation 1:1b-3 --- The Power and Promise of the Revelation of Jesus Christ}
\tableofcontents
\BI
\section*{Notes}
\I  The point of this sermon is:
        \begin{quote} 
        You need to know and obey the Revelation of Jesus Christ.
        \end{quote}
\I  Remember that with every subsection, your job is to answer three questions:
    \begin{enumerate}
    \I  What does it mean?
    \I  Why does it matter?
    \I  How does it change my life?
    \end{enumerate}

\section*{Introduction}
\I  John's prologue underscores the gravity and urgency of Revelation.
\I  The Person of Revelation.
\I  The Purpose of Revelation.

\section{The Power of Revelation}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{A personal eyewitness account}

\section{The Promise of Revelation}
\subsection{What is the blessing?}
\subsection{Who is the blessing for?}
\subsection{What does the blessing mean?}

\EI
\end{document}
